Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-22 ms.tex
editing3

A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.  We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).  Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.  MSP heating is
again found to be negligible.  The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant.  For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.  Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.  Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).   Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see appendix~\ref{app:windheat} for details).}
\end{figure}

The bottom panel of Figure~\ref{fig:vwSources} shows the ratio of
heating to radiative cooling at the stagnation radius
(eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total
heating rate from the top panel Figure \ref{fig:vwSources}.  The
combined heating rate from stellar winds and Compton heating is
insufficient to prevent thermal instability for the high $\Mbh$.
{\bf AG: Should we really be talking about Compton heating stabilizing
the flow}?
% However, if Ia supernovae are included in the schematic way described
% above, the flow again becomes thermally stable for $\Mbh \gtrsim
% XXXX$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
    referring to the first part of the equation here--I use the
    appropriate convolution the Ia rate here}. $\rs$ is calculated
  using the equation~\eqref{eq:stag_simple} and the $\vwO$
  corresponding to each $\Mbh$--see the black line
  Figure~\ref{fig:vwSources}.}
\end{figure}

>>>>

A single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively,
smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.  We estimate the average value of $\vwO$ as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.
Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}; top panel).  Star formation histories are also convolved with the Ia DTD distribution to determine the SN Ia heating.

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.  Again, Ia heating is suppressed when the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in the bottom panel of Figure ~\ref{fig:eta}.  MSP heating is again found to be negligible for all black hole masses.  The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant.  For $\Mbh\gsim 5\times 10^{8} \Msun$, the lack of younger stellar populations reduces the role of stellar wind heating, with Compton heating playing a more important role.  Again, solid and dashed lines show black hole masses for which the flow is thermally stable and thermally unstable, respectively, as shown in the bottom panel.

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.  Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.  Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).   Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}. {\bf BDM: change x axis range so lines start at 3e6 yr }}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:eta} {\it Top panel:} Parameter $\eta$ characterizing stellar mass
  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom panel:} Ratio of Ia radius to stagnation radius as a function of $\Mbh$.  The Ia radius calculated from equation~\eqref{eq:rIa} based on convolving the average star formation histories with the SN Ia DTD.  The stagnation radius is calculated from \eqref{eq:stag_simple} using the total heating rate for each $\Mbh$ shown in the top panel. }
\end{figure}

@@

% However, if Ia supernovae are included in the schematic way described
% above, the flow again becomes thermally stable for $\Mbh \gtrsim
% XXXX$.

@@
